---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lifetables

<!-- badges: start -->
<!-- badges: end -->

The `lifetables` package contains functions that create a life table based on mortality data, and ultimately calculates life expectancy from data on annual deaths for given ages/age groups. This package also contains mortality data from CDC wonder.

## Target audience 

Our target audience for this package are actuaries, epidemiologists, or generally any data scientists working with mortality data.

## R package proposal

We are still working on an R package that has a function for creating lifetables from age-group mortality data, and some included lifetables. We now want to include functions that will result in different combinations of columns from a full lifetable.

## Installation

You can install the development version of lifetables from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("g-rade/lifetables")
```

## How To Use 'lifetables'
```{r}
library(lifetables)

## Take a look at the mortality2 data fram
head(mortality2)


## Use the lifetable function to make a custom life table with just
## CentralDeathRate, PropToSurvive, and LifeExpectancy by setting includeAllSteps = FALSE

lifetable(mortality2, age_group, population, deaths, FALSE, TRUE, TRUE)


## Or show everything by setting includeAllSteps=TRUE, includeCDR=TRUE, and includePS=TRUE which are the default values
lifetable(mortality2, age_group, population, deaths)
```


## Contributors

  + [Grace Rade](https://github.com/g-rade)
  + [Maeve Tyler-Penny](https://github.com/mctp546)
  + [Julia Ting](https://github.com/jtingy)
